Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-17 doc/main_jfm.tex
edited up to end of Section 3

% Bryan's Marcros
\renewcommand{\aa}{\mathbf{a}}
\newcommand{\bd}{\partial}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\eeta}{\boldsymbol{\eta}}
\newcommand{\FF}{\mathbf{F}}
\newcommand{\GG}{\mathbf{G}}
\newcommand{\JJ}{\mathbf{J}}
\newcommand{\nnu}{\boldsymbol{\nu}}
\newcommand{\ttau}{\boldsymbol{\tau}}
\newcommand{\ssigma}{\boldsymbol{\sigma}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\RR}{\mathbf{R}}
\renewcommand{\SS}{\mathbf{S}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\XX}{\mathbf{X}}
\newcommand{\uu}{\mathbf{u}}
\renewcommand{\vv}{\mathbf{v}}
\newcommand{\yy}{\mathbf{y}}
\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Governing  Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
We consider an $N_b$-many body collection of particles suspended in a
two-dimensional unbounded domain $\Omega$. The boundary of each particle is
denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup \Gamma_2 \cup
\cdots \cup \Gamma_{N_b}$ and $\nnu_i$ is the particle outward normal. 
Assuming the flow is Stokesian, the governing
equations are
\begin{alignat}{3}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $\mu$ is viscosity, $p$ is the pressure,
and $\uu_\infty$ is the background flow. Since each particle $\Gamma_i$
with center $\aa_i$ is a rigid body, its velocity satisfies 
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$. Therefore, the no-slip boundary condition on each particle is
\begin{align}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \Gamma_i.
\end{align}
To determine the translational and angular velocities of each particle,
we assume some imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are intertialess, force balance
gives 
\begin{alignat}{2}
  \label{eqn:force}
  \FF_i &+ \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eqn:torque}
  T_i &+ \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu_i) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor).
The process of finding the translational and angular velocities given a
force and torque is referred to as the mobility problem.

\subsection{Imposed Forces}
The imposed forces and torques contain two parts. The first part comes
from the hydrophobic attraction potential (HAP). This potential was
introduced in~\cite{Fu20} and models hydrophobic attraction by solving
the screened Laplace equation boundary value problem
\begin{alignat}{2}
  \label{SL}
-\rho^2 \Delta u + u &=0,            && \xx \in \Omega,\\
\label{SLbc}
u(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i, \\
\label{SLff}
u &\to 0,                          &&|\xx| \to \infty,
\end{alignat}
where $f_i$ is a material label with $f_i = 0$, respectively $1$, representing
hydrophilic, respectively hydrophobic, portions of the surface, and $\rho$ is the
decay length of attraction. The forces and torques for this attraction
are 
\begin{align}
  \label{eqn:hydrophobicAttraction}
  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu_i \, \dif s, 
    \quad 
  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu_i) \dif s,
\end{align}
where
\begin{align}
  \label{eq:stress}
\mathbf{T}
= \gamma\rho^{-1}u^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
  u|^2 \mathbf{I} - \nabla u  \nabla u^T\right)
\end{align}
is the hydrophobic stress tensor. The parameter $\gamma$ is interfacial
tension. The forces $\FF_i^{\text{hydro}}$ and torques
$T_i^{\text{hydro}}$ are responsible for forming particle aggregates
that partially sequester the hydrophobic portions of the particle
surface.

The second part of the imposed forces and torques comes from repulsion
between proximal particles. Given a pair particles indexed with $i$ and
$j$, we find the two points $\tilde{\xx}_i \in \Gamma_i$ and
$\tilde{\xx}_j \in \Gamma_j$ that are closest to one another. We then
define the repulsion force and torque
\begin{align}
%  \label{eqn:REPUL}
%  \FF_i^{\text{repul}} = \sum_{i=1}^{N_b} \frac{\xx_{ij} -
%  \yy_{ij}}{\rho_{ij}} P(\rho_{ij}),\quad 
%  T_i^{\text{repul}} = \sum_{i=1}^{N_b} (\xx_{ij} - \aa_i)^{\perp}\cdot
%  \frac{\xx_{ij} - \yy_{ij}}{\rho_{ij}} P(\rho_{ij})
%  \\
%
  \label{eqn:REPULforce}
  \FF_i^{\text{repul}} &= \sum_{j \neq i} 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
    P'(|\tilde{\xx}_i - \tilde{\xx}_j|), \\
  \label{eqn:REPULtorque}
  T_i^{\text{repul}} &= \sum_{j \neq i} 
    (\tilde{\xx}_i - \aa_i)^{\perp} \cdot 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
    P'(|\tilde{\xx}_i - \tilde{\xx}_j|).
\end{align}
The repulsion profile $P(r)$ is zero for distances $r$ larger than a
repulsion length scale $\rho_0$. As such,~\eqref{eqn:REPULforce}
and~\eqref{eqn:REPULtorque} ignore particles $\Gamma_j$ outside a
tubular neighborhood of $\Gamma_i$. For $0 \leq r < \rho_0,$ we use
$P(r) = M(1 - \sin(r/\rho_0))$ where $M$ is sufficiently large to
prevent particle collisions. Then, the total imposed force and torque
are
\begin{align}
  \FF_i = \FF_i^{\text{hydro}} + \FF_i^{\text{repul}},\quad
  T_i = T_i^{\text{hydro}} + T_i^{\text{repul}}, \qquad
  i=1,\ldots,N_b.
\end{align}

\subsection{Time Marching}
By solving the mobility problem, we obtain translational and angular
velocities of the $N_b$-body system. A second-order Adams-Bashforth
scheme updates the particle positions and orientations. By including the
repulsion force~\eqref{eqn:REPULforce} and
torque~\eqref{eqn:REPULtorque}, particle collisions are avoided even
when using a relatively large time step.

@@

%%%
\section{Integral Equation Method}
\label{sec:IEM}
Computing the hydrophobic attraction potential and the particle forces
and torques requires solving an elliptic partial differential equation
(PDE) in an unbounded complex domain. We recast both these PDEs as
boundary integral equations (BIEs). We discretize each BIE at $N$ points
on each of the $N_b$ particles with a collocation method. Integrals that
are smooth are computed with the spectrally-accurate quadrature rule,
and nearly-singular integrals, caused by close contact between two
particles, are computed with a high-order interpolation-based quadrature
rule~\cite{qua-bir2014}. After discretizing and applying quadrature, the
resulting linear system is solved with matrix-free GMRES, and we
guarantee that the number of GMRES iterations is mesh-independent by
using second-kind BIEs.

\subsection{HAP Boundary Integral Equation}
Similar to our previous work~\cite{Fu20}, we represent the HAP as a
double-layer potential
\begin{align}
  \label{eqn:HAP_DLP}
  u(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \Omega,
\end{align}
where $K_0$ is the zeroth-order modified Bessel function of the first
kind. By requiring that the density function $\sigma$ satisfies the
second-kind integral equation
\begin{equation}
\label{eq:SKIE}
  f(\xx) = \frac{1}{2}\sigma(\xx) + 
    \frac{1}{2\pi}\int_{\bd\Omega} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \bd\Omega,
\end{equation}
the HAP double-layer potential~\eqref{eqn:HAP_DLP} satisfies the
screened Laplace equation~\eqref{SL}--\eqref{SLff}. To calculate the
hydrophobic force and torque, the gradient of the double-layer
potential~\eqref{eqn:HAP_DLP} must be computed on the boundary of each
particle. In Section~\ref{subsec:calculating_force}, we show that the force and
torque calculations can be expressed in terms of integral that are
non-singular.

\subsection{Mobility Problem Boundary Integral Equation}
Following previous work of~\cite{Lukas19}, we represent the velocity as
the sum of a double-layer potential and the $N_b$ Stokeslets and Rotlets
\begin{align}
  \label{eqn:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
\end{align}
The double-layer potential is
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nnu}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) \, \dif s_\yy,
\end{align}
where $\rr = \xx - \yy$ and $\rho = |\rr|$. The Stokeslet and Rotlet
centered at $\aa_i$ are
\begin{align}
  \SS(\xx,\aa_i)\FF_i &= \frac{1}{4\pi} \left(-\log(\rho) + 
    \frac{\rr \otimes \rr}{\rho^2} \FF_i \right), \\
  \RR(\xx,\aa_i)T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{\rho^2} T_i,
\end{align}
where $\rr = \xx - \aa_i$ and $\rho = |\rr|$. The Stokeslet is
torque-free and has force $\FF_i$ while the Rotlet force-free and has
torque $T_i$. Therefore, the velocity~\eqref{eqn:velocity} satisfies the
total force~\eqref{eqn:force} and torque~\eqref{eqn:torque} conditions
if the double-layer potential $\DD[\eeta]$ is force- and torque-free.
Matching the limit of~\eqref{eqn:velocity} with the rigid body motion,
and imposing that $\DD[\eeta]$ is force- and torque-free, the density
function $\eeta$, translational velocity $\vv_i$, and angular velocity
$\omega_i$ satisfy
\begin{alignat}{3}
  \nonumber
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
  \label{eqn:SKIE}
    + \sum_{j=1}^{N_b} &
    \left(\SS(\xx,\aa_j) \FF_j + \RR(\xx,\aa_j) T_j\right),
    \quad &&\xx \in \bd \Gamma_i,\: i=1,\ldots,N_b, \\
  \label{eqn:mobility1}
  \int_{\bd\Gamma_i} \eeta \cdot \nnu_i \, \dif s &= {\bf 0}, 
  &&i = 1,\ldots,N_b, \\
  \label{eqn:mobility2}
  \int_{\bd\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu_i \, \dif s &= 0,
  &&i = 1,\ldots,N_b.
\end{alignat}

The trapezoid rule is used to approximate each of the integrals in
equations~\eqref{eqn:mobility1} and~\eqref{eqn:mobility2}, and the
double-layer potential equation~\eqref{eqn:SKIE} is approximated with
either the trapezoid rule, or the interpolation-based near-singular
integration quadrature rule. After discretizing and applying appropriate
quadrature rules, the result is a $(2NN_b + 3N_b) \times (2NN_b + 3N_b)$
linear system that we precondition with a block-diagonal preconditioner.
We note that other BIE formulations of the mobility problem use
single-layer potentials~\cite{cor-gre-rac-vee2017, rac-gre2016} or both
single- and double-layer potentials~\cite{cor-vee2018}.

\subsection{Calculating the Hydrophobic Force}
\label{subsec:calculating_force}
Once \eqref{eq:SKIE} has been solved and $\sigma$ determined,
we can evaluate the integrals  \eqref{eqn:hydrophobicAttraction}. 
These integrals involve the stress \eqref{eq:stress} which contains
a singular integral for the gradient of the double-layer potential.   
To avoid singular integrals, we use the alternative forms
\begin{equation}
\label{eq:recipforcetorque}
\FF_i^{\text{hydro}} = \int_{\Gamma_i} \JJ_i \,\dif s,\quad
T_i^{\text{hydro}}    = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot \JJ_i  \,\dif s
\end{equation}
where
 \begin{equation}
\label{eq:jumpstress1}
\JJ_{i} =2\gamma\rho^{-1} \sigma v_i \nnu + 2\gamma\rho \frac{d\sigma }{ds}\frac{dv_i }{ds} \nnu
    - 2\gamma\rho \ \frac{d\sigma }{ds} \frac{dv_i }{d\nu} \ttau.
\end{equation}
Here, $\ttau$ and $\frac{d}{ds}$ are the unit tangent  and arc length  derivative for $\Gamma_i$, respectively, 
and
\begin{equation}
\label{eq:uidef}
    v_i(\xx) = u(\xx) - \frac{1}{2\pi} \int_{\Gamma_i} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \Omega.
\end{equation}
The advantage in using \eqref{eq:jumpstress1} over \eqref{eq:stress} 
is that components $\sigma$, $v_i$, $\frac{d\sigma}{ds}$, and  $\frac{dv_i}{ds}$ are all smooth.

To prove \eqref{eq:recipforcetorque},
let \begin{align*}
  {\bf T}
  &=
    \mathbf{S}(u_i,u_i)
  +(\mathbf{S}(u_i,v_i)
  +\mathbf{S}(v_i,u_i))
  +\mathbf{S}(v_i,v_i) \\
  &= {\bf T}_1 + {\bf T}_2 + {\bf T}_3
\end{align*}
where we introduce the bilinear form
\begin{equation}
\label{eq:Tsplit}
\mathbf{S}(u,v)
=  \gamma\rho^{-1} uv {\bf I} + \gamma\rho \nabla u \cdot \nabla v {\bf I} - 2 \gamma \rho \nabla u \nabla v^T .
\end{equation}
Using the fact that $u$,  $u_i$, and $v_i$ solve the equation $-\rho^2 \Delta u + u = 0$,
and that $\mathbf{T}$, $\mathbf{T}_j$, $j = 1, 2, 3$ are symmetric, it is straightforward to verify that 
  \begin{equation}
    \label{eq:decompdivfree}
    \nabla \cdot {\bf T}_j = 0, \quad
    \nabla \cdot ((\xx-\aa_i)^{\perp} \cdot {\bf T}_j) = 0, \quad j = 1, 2, 3.
  \end{equation}

@@

\subsection{Self-Assembly and Relaxation}

@@

%%%

\section{\label{results}Numerical Results}

>>>>

% Bryan's Marcros
\renewcommand{\aa}{\mathbf{a}}
\newcommand{\bd}{\partial}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\eeta}{\boldsymbol{\eta}}
\newcommand{\FF}{\mathbf{F}}
\newcommand{\GG}{\mathbf{G}}
\newcommand{\JJ}{\mathbf{J}}
\newcommand{\nnu}{\boldsymbol{\nu}}
\newcommand{\ttau}{\boldsymbol{\tau}}
\newcommand{\ssigma}{\boldsymbol{\sigma}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\RR}{\mathbf{R}}
\renewcommand{\SS}{\mathbf{S}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\XX}{\mathbf{X}}
\newcommand{\uu}{\mathbf{u}}
\renewcommand{\vv}{\mathbf{v}}
\newcommand{\yy}{\mathbf{y}}
\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\jump}[1]{[\![ #1 ]\!]}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Governing Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
We consider an $N_b$-many body collection of particles suspended in a
two-dimensional unbounded domain $\Omega$. The boundary of each particle
is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup \Gamma_2
\cup \cdots \cup \Gamma_{N_b}$ and $\nnu_i$ is the particle outward
normal. Assuming the inertial terms are negligible, the governing
equations are
\begin{alignat}{3}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $\mu$ is viscosity, $p$ is the pressure,
and $\uu_\infty$ is the background flow. Since each particle $\Gamma_i$
with center $\aa_i$ is a rigid body, its velocity satisfies 
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$. Therefore, the no-slip boundary condition on each particle is
\begin{align}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \Gamma_i.
\end{align}
To determine the translational and angular velocities of each particle,
we define imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are intertialess, force balance
gives 
\begin{alignat}{2}
  \label{eq:force}
  \FF_i &+ \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eq:torque}
  T_i &+ \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu_i) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor).
The process of finding the translational and angular velocities given a
force and torque is referred to as the mobility problem.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Imposed Forces}
The imposed forces and torques contain two parts. The first part comes
from the hydrophobic attraction potential (HAP). This potential was
introduced in~\cite{Fu20} and models hydrophobic attraction by solving
the screened Laplace equation boundary value problem
\begin{alignat}{2}
  \label{eq:SL}
-\rho^2 \Delta u + u &=0,            && \xx \in \Omega,\\
\label{eq:SLbc}
u(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i, \\
\label{eq:SLff}
u &\to 0,                          &&|\xx| \to \infty,
\end{alignat}
where $f_i$ is a material label with $f_i = 0$, respectively $1$, representing
hydrophilic, respectively hydrophobic, portions of the surface, and $\rho$ is the
decay length of attraction. The forces and torques for this attraction
are 
\begin{align}
  \label{eq:hydrophobicAttraction}
  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu_i \, \dif s, 
    \quad 
  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu_i) \dif s,
\end{align}
where
\begin{align}
  \label{eq:stress}
\mathbf{T}
= \gamma\rho^{-1}u^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
  u|^2 \mathbf{I} - \nabla u  \nabla u^T\right)
\end{align}
is the hydrophobic stress tensor. The parameter $\gamma$ is interfacial
tension. The forces $\FF_i^{\text{hydro}}$ and torques
$T_i^{\text{hydro}}$ are responsible for forming particle aggregates
that partially sequester the hydrophobic portions of the particle
surface.

The second part of the imposed forces and torques comes from repulsion
between proximal particles. Given a pair particles indexed with $i$ and
$j$, we find the two points $\tilde{\xx}_i \in \Gamma_i$ and
$\tilde{\xx}_j \in \Gamma_j$ that are closest to one another. We then
define the repulsion force and torque
\begin{align}
%  \label{eq:REPUL}
%  \FF_i^{\text{repul}} = \sum_{i=1}^{N_b} \frac{\xx_{ij} -
%  \yy_{ij}}{\rho_{ij}} P(\rho_{ij}),\quad 
%  T_i^{\text{repul}} = \sum_{i=1}^{N_b} (\xx_{ij} - \aa_i)^{\perp}\cdot
%  \frac{\xx_{ij} - \yy_{ij}}{\rho_{ij}} P(\rho_{ij})
%  \\
%
  \label{eq:REPULforce}
  \FF_i^{\text{repul}} &= \sum_{j \neq i} 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
    P'(|\tilde{\xx}_i - \tilde{\xx}_j|), \\
  \label{eq:REPULtorque}
  T_i^{\text{repul}} &= \sum_{j \neq i} 
    (\tilde{\xx}_i - \aa_i)^{\perp} \cdot 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
    P'(|\tilde{\xx}_i - \tilde{\xx}_j|).
\end{align}
The repulsion profile $P(r)$ is zero for distances $r$ larger than a
repulsion length scale $\rho_0$. As such,~\eqref{eq:REPULforce}
and~\eqref{eq:REPULtorque} ignore particles $\Gamma_j$ outside a
tubular neighborhood of $\Gamma_i$. For $0 \leq r < \rho_0,$ we use
$P(r) = M(1 - \sin(r/\rho_0))$ where $M$ is sufficiently large to
prevent particle collisions. Then, the total imposed force and torque
are
\begin{align}
  \FF_i = \FF_i^{\text{hydro}} + \FF_i^{\text{repul}},\quad
  T_i = T_i^{\text{hydro}} + T_i^{\text{repul}}, \qquad
  i=1,\ldots,N_b.
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Time Marching}
By solving the mobility problem, we obtain translational and angular
velocities of the $N_b$-body system. A second-order Adams-Bashforth
scheme updates the particle positions and orientations. By including the
repulsion force~\eqref{eq:REPULforce} and
torque~\eqref{eq:REPULtorque}, particle collisions are avoided even
when using a relatively large time step.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Integral Equation Method}
\label{sec:IEM}
Computing the hydrophobic attraction potential and the particle forces
and torques requires the solution of elliptic partial differential
equations (PDEs) in an unbounded complex domain. We recast both these
PDEs as boundary integral equations (BIEs). We discretize each BIE at
$N$ points on each of the $N_b$ particles with a collocation method.
Integrals that are smooth are computed with the spectrally-accurate
quadrature rule, and nearly-singular integrals, caused by close contact
between two particles, are computed with a high-order
interpolation-based quadrature rule~\cite{qua-bir2014}. After
discretizing and applying quadrature, the resulting linear system is
solved with matrix-free GMRES, and we guarantee that the number of GMRES
iterations is mesh-independent by using second-kind BIEs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{HAP Boundary Integral Equation}
Similar to our previous work~\cite{Fu20}, we represent the HAP as a
double-layer potential
\begin{align}
  \label{eq:HAP_DLP}
  u(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \Omega,
\end{align}
where $K_0$ is the zeroth-order modified Bessel function of the first
kind. By requiring that the density function $\sigma$ satisfies the
second-kind integral equation
\begin{equation}
\label{eq:screenedSKIE}
  f(\xx) = \frac{1}{2}\sigma(\xx) + 
    \frac{1}{2\pi}\int_{\bd\Omega} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \bd\Omega,
\end{equation}
the HAP double-layer potential~\eqref{eq:HAP_DLP} satisfies the screened
Laplace equation~\eqref{eq:SL}--\eqref{eq:SLff}. We
solve~\eqref{eq:screenedSKIE} with a collocation method. The integrals
are approximated with either the trapezoid rule or with the
interpolation-based near-singular integration scheme. This results in a
$NN_b \times NN_b$ linear system that is solved with a block-diagonal
preconditioned GMRES solver.

To calculate the hydrophobic force and torque, the gradient of the
double-layer potential~\eqref{eq:HAP_DLP} must be computed on the
boundary of each particle. In Section~\ref{subsec:calculating_force}, we
show that the force and torque calculations can be expressed in terms of
non-singular integrals.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mobility Problem Boundary Integral Equation}
Following previous work of~\cite{Lukas19}, we represent the velocity as
the sum of a double-layer potential and $N_b$ Stokeslets and Rotlets
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
\end{align}
The double-layer potential is
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nnu}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) \, \dif s_\yy,
\end{align}
where $\rr = \xx - \yy$ and $\rho = |\rr|$. The Stokeslet and Rotlet
centered at $\aa_i$ are
\begin{align}
  \SS(\xx,\aa_i)\FF_i &= \frac{1}{4\pi} \left(-\log \rho + 
    \frac{\rr \otimes \rr}{\rho^2}\right) \FF_i, \\
  \RR(\xx,\aa_i)T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{\rho^2} T_i,
\end{align}
where $\rr = \xx - \aa_i$ and $\rho = |\rr|$. The Stokeslet is
torque-free and has force $\FF_i$ while the Rotlet is force-free and has
torque $T_i$. Therefore, the velocity~\eqref{eq:velocity} satisfies the
total force~\eqref{eq:force} and torque~\eqref{eq:torque} conditions
if the double-layer potential $\DD[\eeta]$ is force- and torque-free.
Matching the limit of~\eqref{eq:velocity} with the rigid body motion,
and imposing that $\DD[\eeta]$ is force- and torque-free, the density
function $\eeta$, translational velocity $\vv_i$, and angular velocity
$\omega_i$ satisfy
\begin{alignat}{3}
  \nonumber
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
  \label{eq:SKIE}
    + \sum_{j=1}^{N_b} &
    \left(\SS(\xx,\aa_j) \FF_j + \RR(\xx,\aa_j) T_j\right),
    \quad &&\xx \in \Gamma_i,\: i=1,\ldots,N_b, \\
  \label{eq:mobility1}
  \int_{\bd\Gamma_i} \eeta \cdot \nnu_i \, \dif s &= {\bf 0}, 
  &&i = 1,\ldots,N_b, \\
  \label{eq:mobility2}
  \int_{\bd\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu_i \, \dif s &= 0,
  &&i = 1,\ldots,N_b.
\end{alignat}

The trapezoid rule is used to approximate the integrals in
equations~\eqref{eq:mobility1} and~\eqref{eq:mobility2}, and the
double-layer potential equation~\eqref{eq:SKIE} is approximated with
either the trapezoid rule, or the interpolation-based near-singular
integration scheme. After discretizing and applying appropriate
quadrature rules, the result is a $(2NN_b + 3N_b) \times (2NN_b + 3N_b)$
linear system that we precondition with a block-diagonal preconditioner.
We note that other BIE formulations of the mobility problem use
single-layer potentials (\cite{cor-gre-rac-vee2017, rac-gre2016}) or a
combination of single- and double-layer potentials (\cite{cor-vee2018}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Calculating the Hydrophobic Force}
\label{subsec:calculating_force}
Once \eqref{eq:SKIE} has been solved for $\sigma$, we need to evaluate
the integrals~\eqref{eq:hydrophobicAttraction}. These integrals involve
the stress \eqref{eq:stress} which contains a singular integral for the
gradient of the double-layer potential. To avoid singular integrals, we
use the alternative forms
\begin{align}
  \label{eq:recipforcetorque}
  \FF_i^{\text{hydro}} = \int_{\Gamma_i} \JJ_i \,\dif s,\quad
  T_i^{\text{hydro}}    = \int_{\Gamma_i} 
    (\xx - \aa_i)^{\perp} \cdot \JJ_i  \,\dif s,
\end{align}
where
\begin{align}
  \label{eq:jumpstress1}
  \JJ_{i} = 2\gamma\rho^{-1} \sigma v_i \nnu + 
    2\gamma\rho \frac{d\sigma}{ds} \frac{dv_i}{ds} \nnu -
    2\gamma\rho \frac{d\sigma}{ds} \frac{dv_i}{d\nu} \ttau.
\end{align}
Here, $\ttau$ and $\frac{d}{ds}$ are the unit tangent  and arc length
derivative for $\Gamma_i$, respectively, and
\begin{equation}
\label{eq:uidef}
    v_i(\xx) = u(\xx) - \frac{1}{2\pi} \int_{\Gamma_i} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \Omega.
\end{equation}
That is, $\nu_i(\xx)$ is the double-layer potential~\eqref{eq:HAP_DLP},
except that $\Gamma_i$ is excluded from $\bd\Omega$. The advantage in
using \eqref{eq:jumpstress1} over \eqref{eq:stress} is that components
$\sigma$, $v_i$, $\frac{d\sigma}{ds}$, and $\frac{dv_i}{ds}$ are all
smooth.

To prove \eqref{eq:recipforcetorque}, let 
\begin{align*}
  {\bf T} &=
    \mathbf{S}(u_i,u_i)
  +(\mathbf{S}(u_i,v_i)
  +\mathbf{S}(v_i,u_i))
  +\mathbf{S}(v_i,v_i) \\
  &= {\bf T}_1 + {\bf T}_2 + {\bf T}_3
\end{align*}
where we introduce the bilinear form
\begin{equation}
\label{eq:Tsplit}
\mathbf{S}(u,v)
=  \gamma\rho^{-1} uv {\bf I} + \gamma\rho \nabla u \cdot \nabla v {\bf I} - 2 \gamma \rho \nabla u \nabla v^T .
\end{equation}
Using the fact that $u$,  $u_i$, and $v_i$ solve the screened Laplace
equation~\eqref{eq:SL},  and that $\mathbf{T}$, $\mathbf{T}_j$, $j = 1,
2, 3$ are symmetric, it is straightforward to verify that 
  \begin{equation}
    \label{eq:decompdivfree}
    \nabla \cdot {\bf T}_j = 0, \quad
    \nabla \cdot ((\xx-\aa_i)^{\perp} \cdot {\bf T}_j) = 0, \quad j = 1, 2, 3.
  \end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Self-Assembly and Relaxation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{results}Numerical Results}
